\section{\resheading{\textsc{Professional Experience}}}

\vspace{8pt} % Gap between title and text

{\bf Digital Reasoning, Inc. } \hfill {\bf Franklin, TN}

{\sl Technical Product Manager} \hfill {\sl Apr 2018 -- Jan 2019} 
\begin{itemize} 
\item Organized technical and business priorities on backlog for our largest enterprise-level product.
\item Identified process gaps in start-up culture to improve delivery and visibility.
\item Guided engineering teams to better scrum processes for transparency.
\item Created presentations and follow-up processes for reference stories estimation improvements.
%\item Provided a training session on estimation improvements for engineering and product management.
\item Accepted additional role responsibility as scrum master for development teams.
\end{itemize}

\vspace{8pt} % Gap between companies

{\bf Video Gaming Technologies, Inc. - An Aristocrat Company} \hfill {\bf Franklin, TN}

{\sl Engineering Manager} \hfill {\sl Sep 2015 -- Apr 2018} 
\begin{itemize} 
\item Led 15 people with technical design guidance, administrative duties, and professional coaching.
\item Actively engaged in creation of organization’s first Diversity and Inclusion Council.
\item Expanded career development process with personally-researched material to coach direct reports to work outside their comfort zone and achieve greater professional growth.
\item Inspired software engineers' technical skills with engaging activities (i.e., regular competitions, training exercises, structured pair programming, and cross-team mentoring).
\item Conducted regular (weekly and biweekly) one-on-one sessions to develop a close professional relationship with direct reports.
\item Coached direct reports via quarterly performance feedback in addition to official bi-annual performance management schedule.
\item Sponsored a community of practice with up to 30 participating software engineers.
\item Saved the organization \$12-million in contract violation fines during collaborative effort across legacy client teams to complete an unplanned, urgent release one month ahead of schedule.
\item Responsible for recruiting several high-performing individuals at multiple levels on engineering teams with consideration for a diverse team and skill set.
\item Mentored other Engineering Managers on direct report coaching and development.
\item Provided cross-team support for our server system, games team assistance, and big data analysis of casino metrics.
\item Discovered and developed learning opportunities for myself and direct reports -- video courses, podcasts, conferences, on-site activities, and books.
\item Created performance improvement plans to coach under-performing engineers and engaged them to address issues with work output and policy adherence.
\end{itemize}

\vspace{12pt} % Reduce space between positions at the same organization

{\sl Product Owner} \hfill {\sl Jul 2012 -- Sep 2015}
\begin{itemize}
\item Served as Product Management representative during VersionOne implementation, ensuring that the new system reflected business needs for go-live date in Jan 2015.
\item Mentored the team of four other product owners for software and hardware projects.
\item Defined stories and criteria for a Unified Video Platform Proof of Concept (PoC) alongside Aristocrat architects and VGT Engineering Management with an end result noted as "the most complete proof of concept seen to date".
\item Engaged with R\&D to collaboratively create a unique dynamic light controller that doubled player engagement and set our products apart from competitors.
\item Recovered user needs for paytables during relocation and ensured that we met dates for our largest annual trade show despite the loss of all subject matter experts.
\end{itemize} 

%\vspace{2pt} % Reduce space between positions at the same organization

{\sl Software Engineer} \hfill {\sl May 2006 -- Jul 2012} 
\begin{itemize} 
% \item Incorporated new client-server protocols into DOS and Windows platforms to comply with industry communication standards.
% \ 
\item Helped create a cross-department process for the initial stages of requirements management.
\item Collaborated with core application team to refactor device code from C++ to C\(\sharp\).
%\item Guided a project and its technical resources to support a new wiring harness that enabled call-attendant functionality ahead of schedule and with lower technical risk than initially forecast. 
\item Headed the project to implement dynamic printer template system based on Gaming Devices Standards (GDS) printer language.
\item Created an I/O simulator device to save \$200 per platform development kit and increase development efficiency.
\item Achieved the Vice Chair position in the GDS subgroup of the Gaming Standards Association (GSA) (2010-2013).
% \item Implemented 2-Touch Bingo on Client 6, transitioned the project to the development team in OK, and continued to provide technical guidance.
\end{itemize}